Inferential Analysis of the \\ Supreme Court Citation Network

### 2018-01-04 Tex/presentations/SPSA2018/DesmaraisSPSATalk.tex
added daggish visualization

\begin{frame} \frametitle{Captivating Story/Anecdote}

@@

\begin{frame} \frametitle{Citation TERGM}

@@

@@

>>>>

\begin{frame}[plain]% \frametitle{The Importance of Precedent}
\centering

\includegraphics[width = 0.9\textwidth ]{../../images/apsrReference}
\\
\includegraphics[width = 0.9\textwidth ]{../../images/apsrTableScreenshot}
\end{frame}

@@

\frame{
\frametitle{The Exponential Random Graph Model (ERGM)}\vspace{0.5cm}

The probability (likelihood function) of observing network $N$ is:
\[
\mathcal{P}(N, \bt) = \frac{\exp \{ \bt' \bh(N)  \}}{\sum_{N^* \in \mathcal{N}} \exp \{\bt ' \bh(N^*)  \}}
\]
Decomposition:
\[
\underbrace{\bh(N)}_{Net\hspace{3pt} Stats} \qquad \underbrace{\bt}_{Effects} \qquad \underbrace{\exp \{\bt' \bh(N) \}}_{+ \hspace{3pt} Weight} \qquad \underbrace{\sum_{N^* \in \mathcal{N}} \exp \{\bt ' \bh(N^*)  \}}_{Normalizer}
\]

Flexible: $\bh$ can capture virtually any form of interdependence among the edges $+$ covariates\\
\vspace{0.5cm}
Normalizing constant can make estimation difficult
}

\begin{frame} \frametitle{DAG[gish] Dynamics}
\centering

\includegraphics[width = 0.95\textwidth,trim= 0cm 0cm 0cm 1.5cm,clip=true  ]{../../../Tex/images/daggish.pdf}

@@

\begin{columns}
\begin{column}{5cm}
{\bf Exogenous Effects}
\begin{itemize}
\item Ideological Distance
\item Ideological Breadth
\item Same issue
\item Majority size
\item Issue area dummies
\end{itemize}
\end{column}

\begin{column}{6cm}
{\bf Dependence Effects}

\begin{itemize}
\item \# Mutual Dyads
\item \# Transitive Ties
\item \# In-two-stars
\item  \# Out-two-stars
\end{itemize}

\end{column}

@@

{\bf Key Findings}
\begin{enumerate}
\item Citation is characterized by reciprocity and transitivity
\item Dependence effects improve models of citations
\item c-TERGM represents comprehensive method
\end{enumerate}
~\\
{\bf Limitations}
\begin{enumerate}
\item Do not consider the signs of the citations
\item We miss recent terms
\item Case emergence considered exogenous
\end{enumerate}
